### 2015-06-05 chapters/orthography_profiles.tex
wraps line at character width 80 in all tex files

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.} 
	\item \textsc{A minimal profile consists of a single column with header \textsc{graphemes}}, listing each of the different graphemes in a separate line. 
	\item \textsc{Optional columns called `left' and `right' can be used to specify the left and right context of the grapheme, respectively.} The same grapheme can occur multiple times with different contextual specifications, for example to distinguish different pronunciations depending on the context. 
	\item \textsc{The columns `grapheme', `left' and `right' can use regular expression metacharacters.} If regular expressions are used, then all literal usage of the special symbols, like full stops <.> or dollar signs <\$> (so-called \textsc{metacharacters}) have to be explicitly escaped by adding a backslash before them (i.e.~use <.> or <\$>). Note that any specification of context automatically expects regular expressions, so it is probably better to always escape all regular expression metacharacters when used literally in the orthography, i.e.~the following symbols will need to be preceded by a backslash: {[} {]} ( ) \{ \} ~+ * . - ! ? \^{} \$ . 
	\item \textsc{An optional column called `class' can be used to specify classes of graphemes}, for example to define a class of vowels. Users can simply add ad-hoc identifiers in this column to indicate a group of graphemes, which can then be used in the description of the graphemes or the context. The identifiers should of course be chosen such that they do not conflate with any symbols used in the orthography themselves. Note that such classes only refer to the graphemes, not to the context. 
	\item \textsc{Columns describing transliterations for each graphemes can be added and named at will}. Often more than a single possible transliteration will be of interest. Any software application using these profiles should use the names of these columns to select a specific transliteration column. 
	\item \textsc{Any other columns can be added freely, but will mostly be ignored by any software application using the profiles}. As orthography profiles are also intended to be read and interpreted by humans, it is often highly useful to add extra information on the graphemes in further columns, like for example Unicode codepoints, Unicode names, frequency of occurrence, examples of occurrence, explanation of the contextual restrictions, or comments. 
\end{enumerate}

@@

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.} 
	\item \textsc{Each line of a profile will be interpreted as a regular expression. }Software applications using profiles can also offer to interpret a profile in the literal sense to avoid the necessity for the user to escape regular expressions metacharacters in the profile. However, this only is possible when no contexts or classes are described, so this seems only useful in the most basic orthographies. 
	\item \textsc{The `class' column will be used to produce explicit \textsc{or} chains of regular expressions}, which will then be inserted in the `graphemes', `left' and `right' columns at the position indicated by the class-identifiers. For example, a class \textsc{V} as a context specification might be replaced by a regular expression like: (a\textbar{}e\textbar{}i\textbar{}o\textbar{}u\textbar{}ei\textbar{}au). Only the graphemes themselves are included here, not any contexts specified for the elements of the class. 
	\item \textsc{The `left' and `right' contexts will be included into the regular expressions by using lookbehind and lookahead}. Basically, the actual regular expression syntax of lookbehind and lookahead is simply hidden to the users by allowing them to only specify the contexts themselves. Internally, the contexts in the columns \textsc{left} and \textsc{right} are combined with the column \textsc{graphemes} to form a complex regular expression like: (?\textless{}=left)graphemes(?=right). 
	\item \textsc{The regular expressions will be applied in the order as specified in the profile, from top to bottom.} A software implementation can offer help in figuring out the optimal ordering of the regular expressions, but should then explicitly report on the order used. 
\end{enumerate}

>>>>

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.} \item \textsc{A minimal profile
	consists of a single column with header \textsc{graphemes}}, listing
	each of the different graphemes in a separate line.  \item
	\textsc{Optional columns called \textsc{left} and \textsc{right} can be
	used to specify the left and right context of the grapheme,
	respectively.} The same grapheme can occur multiple times with different
	contextual specifications, for example to distinguish different
	pronunciations depending on the context.  \item \textsc{The columns
	\textsc{grapheme}, \textsc{left} and \textsc{right} can use regular
	expression metacharacters.} If regular expressions are used, then all
	literal usage of the special symbols, like full stops <.> or dollar
	signs <\$> (so-called \textsc{metacharacters}) have to be explicitly
	escaped by adding a backslash before them (i.e.~use <.> or <\$>). Note
	that any specification of context automatically expects regular
	expressions, so it is probably better to always escape all regular
	expression metacharacters when used literally in the orthography,
	i.e.~the following symbols will need to be preceded by a backslash: {[}
	{]} ( ) \{ \} ~+ * . - ! ? \^{} \$ .  \item \textsc{An optional column
	called \textsc{class} can be used to specify classes of graphemes}, for
	example to define a class of vowels. Users can simply add ad-hoc
	identifiers in this column to indicate a group of graphemes, which can
	then be used in the description of the graphemes or the context. The
	identifiers should of course be chosen such that they do not conflate
	with any symbols used in the orthography themselves. Note that such
	classes only refer to the graphemes, not to the context.  \item
	\textsc{Columns describing transliterations for each graphemes can be
	added and named at will}. Often more than a single possible
	transliteration will be of interest. Any software application using
	these profiles should use the names of these columns to select a
	specific transliteration column.  \item \textsc{Any other columns can be
	added freely, but will mostly be ignored by any software application
	using the profiles}. As orthography profiles are also intended to be
	read and interpreted by humans, it is often highly useful to add extra
	information on the graphemes in further columns, like for example
	Unicode codepoints, Unicode names, frequency of occurrence, examples of
	occurrence, explanation of the contextual restrictions, or comments.
\end{enumerate}

@@

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.} \item \textsc{Each line of a profile
	will be interpreted as a regular expression. }Software applications
	using profiles can also offer to interpret a profile in the literal
	sense to avoid the necessity for the user to escape regular expressions
	metacharacters in the profile. However, this only is possible when no
	contexts or classes are described, so this seems only useful in the most
	basic orthographies.  \item \textsc{The \textsc{class} column will be
	used to produce explicit \textsc{or} chains of regular expressions},
	which will then be inserted in the \textsc{graphemes}, \textsc{left} and
	\textsc{right} columns at the position indicated by the
	class-identifiers. For example, a class \textsc{V} as a context
	specification might be replaced by a regular expression like:
	(a\textbar{}e\textbar{}i\textbar{}o\textbar{}u\textbar{}ei\textbar{}au).
	Only the graphemes themselves are included here, not any contexts
	specified for the elements of the class.  \item \textsc{The
	\textsc{left} and \textsc{right} contexts will be included into the
	regular expressions by using lookbehind and lookahead}. Basically, the
	actual regular expression syntax of lookbehind and lookahead is simply
	hidden to the users by allowing them to only specify the contexts
	themselves. Internally, the contexts in the columns \textsc{left} and
	\textsc{right} are combined with the column \textsc{graphemes} to form a
	complex regular expression like: (?\textless{}=left)graphemes(?=right).
	\item \textsc{The regular expressions will be applied in the order as
	specified in the profile, from top to bottom.} A software implementation
	can offer help in figuring out the optimal ordering of the regular
	expressions, but should then explicitly report on the order used.
\end{enumerate}
